DATA 621 - Business Analytics and Data Mining

### 2020-11-26 HW5/HW5-Draft.Rmd
I believe this was the only place where dplyr is used. Using base in this one place will prevent package conflicts.

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(mice)
library(pscl)
library(mpath)
library(dplyr)
library(data.table)

@@

Lastly, to handle missing data for `STARS`, they will be replaced by 0, while 
the chemical properties will be imputed. Because the predictive mean matching 
imputation method combines the standard linear regression and the
nearest-neighbor imputation approach, Model Set #2 elected to fill in the
missing values of a continuous variable by using mean-matching imputation.
Afterward, the data is pre-processed to fulfill the assumption of normality
using the Yeo-Johnson transformation (2000). This technique attempts to find the
value of lambda that minimizes the Kullback-Leibler distance between the normal
distribution and the transformed distribution. This method has the advantage of
working without having to worry about the domain of x.

```{r m2clean}
set.seed(525)
m2train <- copy(trnSet[,-1])
m2train[,c(2:8,11:12)] <- abs(m2train[,c(2:8,11:12)])
m2train$STARS[is.na(m2train$STARS)] <- 0
m2train.impute <- mice(m2train, method = 'pmm', print = FALSE)
m2train <- complete(m2train.impute)
m2train.r <- m2train$TARGET
m2train.p <- m2train[,-1]
pre.process <- preProcess(m2train.p, method = c("YeoJohnson"))
m2train.p <- predict(pre.process, m2train.p)
m2train[,c(2:13,15)] <- m2train.p[,c(1:12,14)]
```

@@

```{r model3impute}
set.seed(123)
# ML2 & NB2 data transformation
# MICE imputation on train and test set
m3train <- complete(mice(data = trnSet %>% select(-INDEX),
                         method = "pmm", print = FALSE), 3)
m3test <- complete(mice(data = tstSet %>% select(-INDEX),
                        method = "pmm", print = FALSE), 3)
```

>>>>

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(knitr)
library(MASS)
library(caret)
library(corrplot)
library(mice)
library(pscl)
library(mpath)
library(data.table)

@@

Lastly, to handle missing data for `STARS`, they will be replaced by 0, while 
the chemical properties will be imputed. Because the predictive mean matching 
imputation method combines the standard linear regression and the
nearest-neighbor imputation approach, Model Set #2 elected to fill in the
missing values of a continuous variable by using mean-matching imputation.
Afterward, the data is pre-processed to fulfill the assumption of normality
using the Yeo-Johnson transformation (2000). This technique attempts to find the
value of lambda that minimizes the Kullback-Leibler distance between the normal
distribution and the transformed distribution. This method has the advantage of
working without having to worry about the domain of \(x\).

```{r m2clean}
# P2 & ML 1: Clean and impute
set.seed(525)
m2train <- copy(trnSet[,-1])
m2train[,c(2:8,11:12)] <- abs(m2train[,c(2:8,11:12)])
m2train$STARS[is.na(m2train$STARS)] <- 0
m2train.impute <- mice(m2train, method = 'pmm', print = FALSE)
m2train <- complete(m2train.impute)
m2train.r <- m2train$TARGET
m2train.p <- m2train[,-1]
pre.process <- preProcess(m2train.p, method = c("YeoJohnson"))
m2train.p <- predict(pre.process, m2train.p)
m2train[,c(2:13,15)] <- m2train.p[,c(1:12,14)]
```

@@

```{r model3impute}
# ML2 & NB2 data transformation
# MICE imputation on train and test set
set.seed(123)
m3train <- complete(mice(data = trnSet[, -c('INDEX')],
                         method = "pmm", print = FALSE), 3)
m3test <- complete(mice(data = tstSet[, -c('INDEX')],
                         method = "pmm", print = FALSE), 3)
```
